A Generalized Reduced Linear Program for Markov Decision Processes

### 2016-07-08 resdisc.tex
s.t. abbreviation corrected
Chandru's shortened version

In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
\subsection{On Error Terms}
\begin{itemize}
\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely

@@

The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP. Another interesting feature of our result is that it holds with probability $1$. 
\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance. Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
\end{itemize}
The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
\subsection{On Constraint Reduction and Approximation}
We claim the following based on the error bounds that we derived for the GRLP.\\
{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
\textbf{Main Result~$3$: On Constraint Sampling}\\
The error term $\etmn$ gives new insights into constraint sampling. 

@@

Let $s\in S$ be a state whose constraint was sampled. Then

@@

Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$. However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
\end{proof}\\
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled. Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 

@@

The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 

@@

where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
\subsection{Numerical Illustration}
We take up an example in the domain of controlled queues from \cite{ALP} for which the ALP has been known to work well. For this domain, we make use of our results and observations to select various useful $W$ matrices and present their performance.\\
The queuing system consists of $n=10^4$ states and $d=4$ actions. We chose $n=10^4$ because it was possible to solve both the GRLP and the exact LP (the latter with significant effort) so as to enumerate the approximation errors. We hasten to mention that while we could run the GRLP for queuing systems with $n>10^4$ without much computational overhead, solving the exact LP was not possible for $n>10^4$ as a result of which the approximation error could not be computed.\\
\textbf{Queuing Model:}
The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.\\
\textbf{Choice of $\Phi:$} We make use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}. This takes care of the term $||J^*-\Phi r^*||_\infty$ in \eqref{finalbnd}. \\
\textbf{Selection of $W$:} For our experiments, we choose two contenders for the $W$-matrix and compare them with the ideal sampling matrix $W_i$ (\cite{CS}) and random positive matrix $W_r$. Our choices of the $W$ matrix are as below.\\
{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$. This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.\\
{$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$. Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
\begin{align}\label{wdes}
W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
&=0,\mb\text{otherwise}.
We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
\FloatBarrier
\begin{table}[H]
\begin{center}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|}\hline
Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows values of Error Terms for $Q_L$.}
\label{pref}
\end{table}

\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{center}
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
\subsection{Computational Complexity}
It is known that the complexity of the linear program \cite{karmarkar,adler} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables. In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states. Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states. The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states. We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, while computing the exact solution took about $20$ minutes.
\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
 Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.

>>>>

The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely

@@

The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators. As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability. The error term $\etmn$ gives new insights into constraint selection. 

@@

Let $s\in S$ be a state whose constraint was selected. Then

@@

Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$. However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.\par
The GRLP has linear function approximation in both the primal and dual variables of the LP formulation. To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 

@@

Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approxmation of the Lagrange multipliers. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 

@@

where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

### 2016-07-08 single/abstract.tex
Chandru's shortened version

\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

>>>>

%\begin{comment}
\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
%\end{comment}
\begin{comment}
\begin{abstract}
The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states. An attractive feature of the ALP is that it has fewer number of variables compared to the number of states of the MDP and it offers sound theoretical guarantees. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.
\end{abstract}
\end{comment}
\begin{comment}
\begin{abstract}
The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states. A serious limitation of the ALP is that it has intractable number of constraints. A practical solution is to sample a tractable number constraints of the ALP to formulate a reduced linear program (ALP). In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Unlike prior results on constraint sampling which hold only with high probability, our analysis holds with probability one and is based on a novel contraction operator. 
%In addition to handling linear approximation of the constraints
%We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\end{comment}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

### 2016-07-08 single/concl.tex
Chandru's shortened version

\section{Conclusion}
The approximate linear programming (ALP) is an approximate dynamic programming method that addresses the prediction and control problems successfully. However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP). Though RLP has been found to work well empirically in various domains ranging from queues to Tetris games, performance guarantees are available only in the case of a specific RLP formulated under idealized assumptions. Thus there has been a gap in the theory of constraint reduction.\\
In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction. The constraints of the GRLP were obtained as positive linear combinations of the original ALP. We provided an error bound that relates the optimal value function to the solution of the GRLP. Our error bound contained two terms, one inherent to the ALP formulation and the other due to constraint reduction. We also made qualitative and quantitative observations about the nature of the error term that arose due to constraint reduction. Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work. In particular, we also theoretically justified linear function approximation of the constraints. We also discussed the results and provided a numerical example in the domain of controlled queues. To conclude, we observe that by providing a novel theoretical framework to study constraint approximation, this paper provides important results that add to the theory of ALP.

>>>>

\section{Conclusion}
The approximate linear programming (ALP) is a widely employed method to handle MDPs with large number of states. However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP). The RLP has been found to work well empirically in various domains ranging from queues to Tetris games, and performance guarantees are for a specific RLP formulated under idealized assumptions. Alternatively, function approximation in the dual variables of the ALP has been another approach that has been employed in literature \cite{ALP-Bor,dolgov} to address the issue of large number of constraints. However \cite{ALP-Bor,dolgov} do not provide theoretical characterization for the function approximation of the dual variables.\par
In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction. The constraints of the GRLP were obtained as positive linear combinations of the original ALP. We provided an error bound that relates the optimal value function to the solution of the GRLP. Our error bound contained two terms, one inherent to the ALP formulation and the other due to constraint reduction. We also made qualitative and quantitative observations about the nature of the error term that arose due to constraint reduction. Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work. In particular, we also theoretically justified linear function approximation of the constraints. We also discussed the results and provided a numerical example in the domain of controlled queues. To conclude, we observe that by providing a novel theoretical framework to study constraint approximation, this paper provides important results that add to the theory of ALP.

### 2016-07-08 single/constsamp.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Constraint sampling}
One way to reduce the number of constraints is to randomly choose a subset of them \cite{CS},
leading to the so-called reduced linear program (RLP). \todoc{How about the results of Calafiore and Campi (2005, Math. Prog.) and others reviewed in \cite{CS}? Any follow-up we missed?}
While the objective function of the RLP is the same as that of the ALP, 
the RLP has only $m \ll nd$ constraints sampled from the original ALP according to a given probability distribution:
\begin{align}\label{rlp}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
\end{split}
\end{align}
where $\I$ is the index set containing $m$ sampled state-action pairs and
the extra constraint set $\N\subset \R^k$ is introduced to guarantee a bounded feasible set (hence, bounded solution).
It is assumed that $\N$ is compact and $\tr\in \N$. \todoc{How can one arrange for this in general?}
The index set $\I$ naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i \eqdef s_i+(a_i-1)\times n$, $i=1,\ldots,m$. Define the constraint sampling matrix $\M \in \R^{nd\times m}$ associated with the index set $\I$ by
\begin{align}
\M(i,j)
=
\begin{cases}
1, & \text{ if } q_i = j\,;\\
0, & \text{ otherwise}.
\end{cases}
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
\end{split}
\end{align}
Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Constraint sampling}
One way to reduce the number of constraints is to randomly choose a subset of them \cite{CS},
leading to the so-called reduced linear program (RLP). \todoc{How about the results of Calafiore and Campi (2005, Math. Prog.) and others reviewed in \cite{CS}? Any follow-up we missed?}
While the objective function of the RLP is the same as that of the ALP, 
the RLP has only $m \ll nd$ constraints sampled from the original ALP according to a given probability distribution:
\begin{align}\label{rlp}
\min_{r\in \N}\, &c^\top \Phi r\nn\\
\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \nn\\
&\forall (s,a) \in \I.
\end{align}
where $\I$ is the index set containing $m$ sampled state-action pairs and the extra constraint set $\N$ is introduced to guarantee a bounded solution. Further we assume that the following holds:
\begin{assumption}\label{nassump}
$\N \subset \R^k$ is compact and $\tr \in \N$.
\end{assumption}
The index set $\I$ in \eqref{rlp} naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i \eqdef s_i+(a_i-1)\times n$, $i=1,\ldots,m$. Define the constraint sampling matrix $\M \in \R^{nd\times m}$ associated with the index set $\I$ by
\begin{align}
\M(i,j)
=
\begin{cases}
1, & \text{ if } q_i = j\,;\\
0, & \text{ otherwise}.
\end{cases}
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
\end{split}
\end{align}
Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.
